The Hajada Imputation Test

### 2020-05-29 article.Rmd
Omg miejmy to już za sobą

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

@@

In this chapter which we decided to name *The Hajada Imputation Test* (taken from the first two letters of creators' names) we'll take a look at several popular imputation methods and try to compare them with each other, including ranking of algorithms taken into account and finally choosing the best one. Obviously its result will not be the final verdict declaring which imputation algorithm is clearly better or worse, but considering the comparison of their quality on different datasets, we will be able to assess their collective performance and effectiveness against the backdrop of the whole. For this purpose, we'll test the modified collections for getting rid of empty values on several machine learning classification algorithms, and then considering the selected quality measures after comparing the results, we'll get the desired view. Due to the need to obtain a clear and interpretable result, we have limited ourselves to the problem of binary classification.

@@

In order to read all datasets we used another function, which returned a dataframe containing all the important informations about the test matrices.

TODO: trochę o metodzie, o funkcjach czytających; PARALLEL, itd

@@

In order to test the same test-train splits we'll use one random seed 1357 for all datasets.

For each machine learning model after every imputation we will get the confusion matrix and the values of four basic metrics:

@@

These four will give us good information about the quality of imputation and give us a good comparison. We get simple and clear information about which observations are well classified, which ones are wrong and how they should be. Considering the number of sets to consider and their different properties, even when it comes to balancing, comparing these four measures, the fact that it will show the pros and cons of given imputations, will additionally be good to compare them.

TODO: MCC jeszcze, czemu f1

## Imputation results

The results of our work will be checked using the implemented classification tree algorithm from the *rpart* package. We have chosen this algorithm because this classifier works well for almost any type of data - and for the most part numerical, and for the most part factors, it can handle and make a decent model. The use of an algorithm using, for example, the distance from the nearest points or separating sets by clusters would not be recommended for each data frame, and given the diversity, here rpart should do a good job.

Also, it is worth mentioning that removing rows computes a different dataset compared to other techniques. Because of that one needs to be cautious while analysing and comparing remove_rows to other imputation methods. For one's own research it is probably worth replacing removing rows with removing columns for datasets with few features containing missing values. 
Here are the results. NA indicates that method returned error:

@@

Let's build a dataframe containing information about imputation methods.

Looks good! Now it's visualization time.

Judging by the logarithmic scale, no surprise removing rows and median replenishment are definitely the fastest methods, with removing rows being several times faster. Looking at more advanced ones, definitely *VIM* rules - probably usually something like 5-10 times faster than *mice* and *missForest*. These last two are quite slow, with the missforest appearing to be slightly faster.

What do the numbers say?

Taking into account all the imputations which have been implemented, we can clearly see that two easy ones really stand out. However, we cannot fully compare the other three - due to the fact that missForest failed on three data sets, and mice - up to seven.

@@

Let's count these four measures again, but only for those datasets for which all imputations were successful - these are ids 27, 38, 55, 56, 944, 188  (dataset with id 4 softened on removing rows containing any missing items, because each of its poems had some missing items).

Now we have better results to compare. Taking into account the mean time, definitely *missForest* is the slowest, but also its standard deviation is incomparably huge - this is probably due to the fact that for smaller sets it is doing well, but due to its complexity, its slowdown can be seen for very large datasets. As shown in the chart, *VIM* is definitely better for quick calculations than *missForest* and *mice*, and considering the median, *mice* is comparable to *missForest* - so you can expect that for small data sets there is not much difference between them, and a lot of time we definitely need to devote to these larger data frames.

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
getwd()
```

@@

In this article which we decided to name *The Hajada Imputation Test* (taken from the first two letters of creators' names) we'll take a look at several popular imputation methods and try to compare them with each other, including ranking of algorithms taken into account and finally choosing the best one. Obviously its result will not be the final verdict declaring which imputation algorithm is clearly better or worse, but considering the comparison of their quality on different datasets, we will be able to assess their collective performance and effectiveness against the backdrop of the whole. For this purpose, we'll test the modified collections for getting rid of empty values on several machine learning classification algorithms, and then considering the selected quality measures after comparing the results, we'll get the desired view. Due to the need to obtain a clear and interpretable result, we have limited ourselves to the problem of binary classification.

@@

In order to read all datasets we used another function, which returned a dataframe containing all the important informations about the test matrices. The generated frames of imputation results and times were saved using parallel processing^9^.

@@

In order to test the same test-train splits we used random seed 1357 for all datasets. For each machine learning model after every imputation was created confusion matrix and the values of four basic metrics:

@@

... in the final conclusion the final ranking concerned only the last one. Additionally, Matthews correlation coefficient measures were also counted.

${\displaystyle {\text{MCC}}={\frac {{\mathit {TP}}\times {\mathit {TN}}-{\mathit {FP}}\times {\mathit {FN}}}{\sqrt {({\mathit {TP}}+{\mathit {FP}})({\mathit {TP}}+{\mathit {FN}})({\mathit {TN}}+{\mathit {FP}})({\mathit {TN}}+{\mathit {FN}})}}}}$

These two gave good information about the quality of imputation and a good comparison. I resulted in simple and clear information about which observations are well classified, which ones are wrong and how they should be. Considering the number of sets to consider and their different properties, even when it comes to balancing, comparing these four measures, the fact that it will show the pros and cons of given imputations, will additionally be good to compare them.

@@

A dataframe containing information about imputation methods was built.

![](files/imputationTimesScatter.png)

Judging by the logarithmic scale, no surprise removing rows and median replenishment are definitely the fastest methods, with removing rows being several times faster. what would you expect, also "random rows" was quite fast, but slower than the two mentioned.Looking at more advanced ones, definitely *VIM* turned up to be the fastest - probably usually something like 5-10 times more than *mice* and *missForest*. These last two are quite slow, with the missforest appearing to be slightly faster.

To better view a boxplot was also created.

![](files/imputationTimesBoxplot.png)

Taking into account all the imputations which have been implemented, we can clearly see that two first mentioned ones really stand out. However, we cannot fully compare the other three - due to the fact that missForest failed on three data sets, and mice - up to seven.

@@

TO NIŻEJ SIĘ NIE PRZYDA CHYBA, ŚCIEK Z PD2
Let's count these four measures again, but only for those datasets for which all imputations were successful - these are ids 27, 38, 55, 56, 944, 188  (dataset with id 4 softened on removing rows containing any missing items, because each of its poems had some missing items).

Now we have better results to compare. Taking into account the mean time, definitely *missForest* is the slowest, but also its standard deviation is incomparably huge - this is probably due to the fact that for smaller sets it is doing well, but due to its complexity, its slowdown can be seen for very large datasets. As shown in the chart, *VIM* is definitely better for quick calculations than *missForest* and *mice*, and considering the median, *mice* is comparable to *missForest* - so you can expect that for small data sets there is not much difference between them, and a lot of time we definitely need to devote to these larger data frames.
NOOO CHYBA MOŻNA WYRZUCIĆ

@@

*^9^parallel: Support for parallel computation, including by forking (taken from package multicore), by sockets (taken from package snow) and random-number generation*

*^10^Matthews correlation coefficient: a measure of the quality of binary (two-class) classifications, introduced by biochemist Brian W. Matthews in 1975*
